\textls[-0]{\thetitle}

### 2023-03-05 metatheory-condensed.tex
Fix typo.

We illustrate one concrete example in \cref{fig:Wtype-example} of a "tm" with only two constructors, 
also as a review for how W-type encodes a given inductive type. The key insight 
is for a pair $(\wsigproj{i}{1}{\wsig}, \wsigproj{i}{2}{\wsig})$, the non-recursive
part of the given constructor stores in $\wsigproj{i}{1}{\wsig}$ and the ``arity'' of the 
recursive part stores in $\wsigproj{i}{2}{\wsig}$. For example, $"app" : ("tm" \to "tm" \to "tm")$ 
$\cong ((\bbtwo \to "tm") \to "tm")$, saying the ``arity'' of the recursive part is $\bbtwo$ 
(or boolean type, as a type with two elements). Similarly, the ``arity'' of recursive part of "unit" is 0. 
Both constructors don't store other information thus $\bbone$. We hightlight $\tau$ as the 
signature of our "tm" and showcase the meta-theoretic encoding of "unit" and "app~unit~unit". $"elim-"\bbzero$ indicates the elimination of the bottom type $\bbzero$ in the context. The expressiveness of W-types comes from the ``arity'', as it encodes the case when recursive structure stores as the output of a function, mirroring the strict-positivity of Inductive type.

>>>>

We illustrate one concrete example in \cref{fig:Wtype-example} of a "tm" with only two constructors, 
also as a review for how W-type encodes a given inductive type. The key insight 
is, to encode one constructor into a pair $(\wsigproj{i}{1}{\wsig}, \wsigproj{i}{2}{\wsig})$, the non-recursive part will be stored in $\wsigproj{i}{1}{\wsig}$ 
while the ``arity'' of the  recursive part stores in $\wsigproj{i}{2}{\wsig}$. 
For example, $"app" : ("tm" \to "tm" \to "tm")$ 
$\cong ((\bbtwo \to "tm") \to "tm")$, saying the ``arity'' of the recursive part is $\bbtwo$ 
(or boolean type, as a type with two elements). Similarly, the ``arity'' of recursive part of "unit" is 0. 
Both constructors don't store other information thus $\bbone$. We hightlight $\tau$ as the 
signature of our "tm" and showcase the meta-theoretic encoding of "unit" and "app~unit~unit". $"elim-"\bbzero$ indicates the elimination of the bottom type $\bbzero$ in the context. Generally speaking, the expressiveness of W-types comes from the ``arity'', as it encodes the case when recursive structure stores as the output of a function, mirroring the strict positivity of Inductive type.
